The Adaptive Multi-scale Simulation Infrastructure - Design and Application

### 2016-01-27 doc/articles/amsi_biotissue/paper.tex
cleanup of process set code, and examination of responsibilities of the process set for eventual removal in lieu of the new RankSet designed for dynamic process reallocation

Typically simulation flow control is determined solely by a runtime system.
A framework may also limit specific features of the numerical implementation to those provided by the framework.
This includes domain discretization models and associated adaptive processes -- structured and unstructured meshing and associated refinement algorithms, particle-in-cell methods, etc. -- convergence algorithms for both the minimization of the relevant residuals (Newton-Raphson, etc.) as well as iterative solution of the resulting linear system (KSP, GMRES, ILU, etc.).

>>>>

%Typically simulation flow control is determined solely by a runtime system.
%A framework may also limit specific features of the numerical implementation to those provided by the framework.
%This includes domain discretization models and associated adaptive processes -- structured and unstructured meshing and associated refinement algorithms, particle-in-cell methods, etc. -- convergence algorithms for both the minimization of the relevant residuals (Newton-Raphson, etc.) as well as iterative solution of the resulting linear system (KSP, GMRES, ILU, etc.).
